
\cvsection{Education}

\begin{cventries}

  \cventry
    {MPhill in Geoscience} % Degree
    {Chinese Academy of Science, Institute of Tibetan Plateau Research} % Institution
    {Beijing, CN} % Location
    {Sep. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Focus:} Probabilistic Machine Learning (Automatic annual layer identification in ice core dating). Supervised by Prof. Yao Tandong and funded by the 2nd scientific investigation on the Tibetan Plateau (2019QZKK0602).}
      \end{cvitems}
    }

%  \cventry
%    {MPhil in Management} % Degree
%    {University of Cambridge} % Institution
 %   {Cambridge, UK} % Location
%    {Oct. 2016 - Jun. 2017} % Date(s)
 %   {
 %     \begin{cvitems} % Description(s) bullet points
 %       \item {Commendation (70\%). \textbf{Focus:} Strategic Valuation (top prize), Economics. \textbf{Audits:} Measure Theory, Philosophy of Science, Physics.}
 %       \item {Jaguar Land Rover consulting project: Modeled the contribution of JLR to the UK economy in a highly collaborative setting. Conducted \textbf{original research} on improving the accuracy of input-output multipliers. Highly commended for the work and presentation.}
%        \item {Coloplast Internship (Aug. '17): Aided implementation of a time series forecasting model (involving splines, linear filters and ARIMA error processes) and automated model fitting.}
%      \end{cvitems}
%    }

  \cventry
    {BSc Hons in Engineering, \textbf{Urban Planning Major}} % Degree
    {Beijing Normal University, Zhuhai Campus} % Institution
    {Zhuhai, CN} % Location
    {Sep. 2017 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Awards:} Distinction (86\%) (top 2\%), Outstanding Student Leaders (2019-2020), Provincial Project Establishment-National College Students Innovation and Entrepreneurship Project (2020-2021) (UPSoc President, Student Union Exec). }
        \item {\textbf{Focus:} Building Information Management(BIM), GIS, urban economics, Quantitative Risk Management. \textbf{Project Areas:} Customs Port Design using BIM, Analysis of relocation and resettlement risks for national park, Coastal line protection strategies,rural construction guidelines. }
      \end{cvitems}
    }

  \vspace{-5mm}

\end{cventries}
