
\cvsection{Employment/Internship}

\begin{cventries}

  \cventry
    {Assistant Planner + Statistician} % Job title
    {Provincial Urban Planning and Design Institute} % Organization
    {Guangzhou, CN} % Location
    {Sep. 2020 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Focusing on building and maintaining end-to-end infrastructure/tech related solutions. This involved data cleaning, analysis, and modeling of regional layouts, environmental impact assessments(e.g., facilitating the implementation of a geospatial data integration platform using ArcGIS Server, which enabled real-time data analysis and collaboration across multiple project sites), and sustainable development strategies (using MATLAB, ArcGIS, and SketchUp). Also engaged in drafting project documentation and client presentations.}
        \item {On the geo-modeling side, I've used GIS and GeoDetector for spatial analysis and risk assessment in urban planning projects, applying spatial statistical models(Geosus-FLUS) to predict and manage the impacts of urban development on local ecosystems. Additionally, I've employed stochastic models to assess the feasibility and impacts of infrastructure projects, including Monte Carlo simulations for cost and risk analysis in large-scale urban redevelopment. }
      \end{cvitems}
    }

  \cventry
    {Data Analyst + Model Developer} % Job title
    {Guangdong-Hong Kong-Macao Port Research Center} % Organization
    {Zhuhai, CN} % Location
    {Oct. 2019 - June. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and produce large-scale BIM models for flow and traffic balance in customs halls, accounting for pedestrian behavior and evolving trends. Modelling primarily depends on Revit, SketchUp, and AutoCAD.}
        \item {In addition to this, I assisted with and reviewed other model implementations (e.g. for current accounts, savings and mortgages). I also piloted new tools, created knowledge-bases, worked on automation and performed exploratory work to identify areas of efficiency (e.g. with Spark, Rcpp, Docker). In some cases, I reduced execution times from days to seconds.}
      \end{cvitems}
    }

\end{cventries}
