
\cvsection{Side Projects}

\begin{cvskills}

  \cvskill{Web}
  {\href{https://www.falmity.com}{falmity.com:} Personal projects (e.g. speech synthesis using Gaussian processes) and minimal examples (e.g. MGCV GAMs as GPs, the Griffin-Lim algorithm, sparse GPs, state-space models). \href{https://stats.stackexchange.com/users/211930/infprobscix}{Cross Validated}: (Stats Stack Exchange) top 2\% contributor in 2018.}

  \cvskill{Code}
  {Contributed to Guangdong(Province) comprehensive urban and rural planning guidelines, SraitiCounter (added a GUI visual interaction page and fixed a few bugs) . Co-wrote the code for the paper below , applied Geodetector and Geosus-Flus model for spatial analysis of habitat quality improvements linked to historical land-use policies.}

  \cvskill{Papers}
  {\item Lalchand, V., \textbf{Ravuri, A.} and Lawrence, N. D. (2020). \textit{Variational Gaussian Process Latent Variable Models with Normalising Flows}. A smaller part of the work titled \href{https://openreview.net/pdf?id=zaMwvOjsyym}{"GPLVFs for Massively Missing Data"} was accepted at AABI 2021.}
  

\cvskill{Papers}
{
  \item \textbf{Luo Y. Q.}, Wang W.\textit{Spatiotemporal Heterogeneity and Influence Factors of Habitat Quality: A Case Study of Golog}. Anthropocene. Under Review
  \item \textbf{Luo Y. Q.}, Yao T., Xu B., Yang D., Wang L., Wu G., Li Z., Wang N., Qu D., Wu X. (2023). \textit{Application of Automatic Annual Layer Identification Method in Ice Core Dating on the Tibetan Plateau}. Journal of Glaciology and Geocryology. Accepted for publication.
  \item \textbf{Luo Y. Q.}, Zhang W. J. (2023).(Conference Paper) \textit{A Community Household Waste Recycling and Classification System Under the Study of Zero-Waste Management}. Proceedings of the International Workshop on Geography and Sustainability: Smart Cities and Sustainability in Comparative Perspective, p. 16785. Conference Paper.
  \item Yu Y. F., \textbf{Luo Y. Q.}, Wang S. J. (2023). \textit{Characteristics of Lake Ice Phenology in Tibetan Plateau and Analysis of Influencing Factors}. International Symposium on Third Pole Environment. Conference Paper.
   }


% languages

\end{cvskills}

% \cvsection{Projects}

% \begin{cventries}

%   \cventry
%     {} % Role
%     {Blog on Statistics} % Title
%     {} % Location
%     {} % Date(s)
%     {
%       \begin{cvitems} % Description(s)
%         \item {...}
%       \end{cvitems}
%     }

% \end{cventries}
